Supplementary Information: Quantifying the pathways to life using assembly spaces

### 2021-05-22 papers/assembly/I/main.tex
Finish the last of the examples

It is natural, once a mathematical structure has been defined, to ask how two instantiations of that structure may be mapped to one another.
There is, of course, a well defined notion of a map between Petri nets, termed here a \textit{Petri net morphism}, which maps sites and transitions of one Petri net into another in a way that is compatible and consistent with the source and target maps of both Petri nets.
These Petri net morphisms will play a crucial roll in the establishment of bounds for the assembly index in \Cref{subsec:assembly-index-bounds}.

@@

{
\color{red}
\TODO{Rework this text}
The ligation example admits a choice of basis: $\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$.
While it may seem undesirable, on its face, for a Petri net to admit more than one basis, there is little difference between this and being able to choose the basis of a vector space such as $\R^2$.
We can view each choice of basis as representing a minimal set of starting components from which everything of interest can be constructed; similar to deciding which raw materials to use to build a house, or which chemical reagents to use to synthesis a given set of molecules.
Depending on the context, there may be \textit{a priori} reasons to prefer one basis over another.
For example, in the ligation example, the $\{A,B,C\}$ basis seems somehow preferable as it is composed of monomers while all other bases consist of higher-order components.
To make such a distinction, however, requires additional structure, such as a grading\footnote{Here we use the term \textit{grading} loosely. It could, for example, simply mean a map $g : S(P) \rightarrow \N$ for some Petri net $P$ which is consistent in some way with the graph structure of $P$.} on the sites with which to formally distinguish between bases.
The choice of basis will become important in \Cref{sec:assembly-spaces,sec:assembly-index}, but for now we are only interested in the existence and uniqueness of bases and their preservation under Petri net morphisms.
For this reason, we will leave the question of mechanisms for preferentially choosing a basis for a future work.

Whether or not a Petri net admits a basis at all and whether that basis is unique, are both fundamentally important questions.
The establishment of something like the assembly index of an object relies on the specification of a basis.
Fortuitously, every Petri net admits at least one basis, and in certain cases this basis will be unique.
\begin{lemma}\label{lem:bases-exist}
    Every Petri net admits at least one basis.
\end{lemma}
\begin{proof}
    \TODO{Complete (likely to use Zorn's lemma)}
\end{proof}
}

@@

As an example of an assembly map, we can use the example map from the Petri net section:
\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}\label{ex:map}
            \begin{pgfonlayer}{nodelayer}
                \node [scale=3] (P) at (12, 0) {$\A$};
                \node [style=site, fill=blue!20] (A) at (0, 0.8) {$A$};
                \node [style=site, fill=blue!20] (B) at (0, -0.8) {$B$};
                \node [style=site, fill=blue!20] (C) at (6, -1.6) {$C$};
                \node [style=site] (AA) at (4, 0.8) {$AA$};
                \node [style=site] (AB) at (4, -0.8) {$AB$};
                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
                \node [style=transition] (tau4) at (10, 0) {$\delta$};

                \node [scale=3] (Q) at (12, -6) {$\C$};
                \node [style=site, fill=blue!20] (W) at (-4, -6) {$W$};
                \node [style=site] (X) at (0, -6) {$X$};
                \node [style=site] (Y) at (4, -6) {$Y$};
                \node [style=site] (Z) at (8, -6) {$Z$};
                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
                \node [style=transition] (tau6) at (2, -6) {$\chi$};
                \node [style=transition] (tau7) at (6, -6) {$\psi$};
                \node [style=transition] (tau8) at (10, -6) {$\omega$};

@@

                \draw [style=sitemap, bend right=30] (A) to (X);
                \draw [style=sitemap, bend right=30] (B) to (X);
                \draw [style=sitemap, bend right=30] (AA) to (Y);
                \draw [style=sitemap, bend right=30] (AB) to (Y);
                \draw [style=sitemap, bend right=30] (C) to (Y);
                \draw [style=sitemap, bend right=30] (AAAB) to (Z);
                \draw [style=transitionmap, bend right=30] (tau1) to (tau6);
                \draw [style=transitionmap, bend right=30] (tau2) to (tau6);
                \draw [style=transitionmap, bend right=30] (tau3) to (tau7);
                \draw [style=transitionmap, bend right=30] (tau4) to (tau8);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}
were we've chosen $\{A,B,C\}$ and $\{W\}$ as the generating sets (in fact, bases) for $\A$ and $\C$, respectively.  
Of particular note here is that $\A$ is certainly a subspace of $\C$, though it is decidedly not rooted in $\C$.
In fact, it will always be the case that the image of an assembly space will be a subspace of the codomain.
\begin{theorem}\label{lem:assembly-image-is-subspace}
    If $f : A \rightarrow B$ is an assembly map between assembly spaces $A$ and $B$, then $f(A)$ is an assembly subspace of $B$.
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}

Exploring the previous example a bit more, by highlighting a rooted subspace of $\A$ we see that the image of that subspace is rooted in the image of $\A$ in $\C$.

\TODO{Example Figure}

This too will always be the case: the image of a rooted subspace will always be rooted in the image.
\begin{theorem}\label{thm:rooted-image}
    Let $A$ be an assembly space, $Z \subseteq A$ a rooted assembly subspace, and $f : A \rightarrow B$ an assembly map.
    Then $(f(Z), S(f)(G_Z))$ is rooted in $(f(A), S(f)(G_A)$.
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}
The interaction of assembly maps and rooted subspaces will allow us to establish bounds on the assembly index, defined in the next section, by considering the image of the space under some map.
These bounds will be useful in situations where determining the assembly index of some object is computationally infeasible.

@@

To conclude this section, we present the assembly index of every site of in our ligation model $\A$ together with a minimal, rooted assembly subspace containing that site.

\TODO{Complete Figure}

In the next section, we will consider methods for bounding the assembly index of a site.

\subsection{Computability of and Bounds on the Assembly Index}\label{subsec:assembly-index-bounds}

The first task, when presented with an assembly space, is to determine the assembly index of the sites in the space.
In practical terms, this requires an algorithm for computing the assembly index relative to some space.
In this work, we do not present a general algorithm to do so, though a simple depth-first search of the space may suffice in some cases.
Rather, we first show that the assembly index is in fact computable.
\begin{theorem}\label{thm:computable}
    If $A$ is an assembly space and $x \in S(A)$ is finite, then $c(x)$ is computable.
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}
Of course, just because the value is computable does not mean that it can be computed in reasonable time.
In fact, the general problem is likely to be \texttt{NP}-hard.
In situtations where direct computation is infeasible, we can resort to bounding the value of the assembly index by computing the index in an analogous space.
The first of the bounds we present is an upper bound determined by computing the assembly index in a subspace containing the site.
\begin{theorem}\label{thm:subspace-index-upper-bound}
    Let $(A, G_A)$ be an assembly space and let $(B, G_A)$ be a rooted assembly subspace of $A$.
    For every finite $b \in S(B)$, the assembly index of $b$ in $B$ is at least the assembly index of $b$ in $A$.
    That is, $c_B(b) \ge c_A(b)$ for all $b \in S(B)$
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}

\TODO{Example and Figure}

>>>>

It is natural, once a mathematical structure has been defined, to ask how two instantiations of that structure may be mapped to one another.
There is, of course, a well defined notion of a map between Petri nets, termed here a \textit{Petri net morphism}, which maps sites and transitions of one Petri net into another in a way that is compatible and consistent with the source and target maps of both Petri nets.
These Petri net morphisms will play a crucial roll in the establishment of bounds for the assembly index in \Cref{sec:assembly-index}.

@@

The ligation example admits a choice of basis: $\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$.
While it may seem undesirable, on its face, for a Petri net to admit more than one basis, there is little difference between this and being able to choose the basis of a vector space such as $\R^2$.
We can view each choice of basis as representing a minimal set of starting components from which everything of interest can be constructed; similar to deciding which raw materials to use to build a house, or which chemical reagents to use to synthesis a given set of molecules.
Depending on the context, there may be \textit{a priori} reasons to prefer one basis over another.
For example, in the ligation example, the $\{A,B,C\}$ basis seems somehow preferable as it is composed of monomers while all other bases consist of higher-order components.
To make such a distinction, however, requires additional structure, such as a grading\footnote{Here we use the term \textit{grading} loosely. It could, for example, simply mean a map $g : S(P) \rightarrow \N$ for some Petri net $P$ which is consistent in some way with the graph structure of $P$.} on the sites with which to formally distinguish between bases.
The choice of basis will become important in \Cref{sec:assembly-spaces,sec:assembly-index}, but for now we are only interested in the existence and uniqueness of bases and their preservation under Petri net morphisms.
For this reason, we will leave the question of mechanisms for preferentially choosing a basis for a future work.

Whether or not a Petri net admits a basis at all and whether that basis is unique, are both fundamentally important questions.
The establishment of something like the assembly index of an object relies on the specification of a basis.
Fortuitously, every Petri net admits at least one basis, and in certain cases this basis will be unique.
\begin{lemma}\label{lem:bases-exist}
    Every Petri net admits at least one basis.
\end{lemma}
\begin{proof}
    \TODO{Complete (likely to use Zorn's lemma)}
\end{proof}

@@

As an example of an assembly map, we can use the example map from the Petri net section:
\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [scale=3] (P) at (12, 0) {$\A$};
                \node [style=site, fill=blue!20] (A) at (0, 0.8) {$A$};
                \node [style=site, fill=blue!20] (B) at (0, -0.8) {$B$};
                \node [style=site, fill=blue!20] (C) at (6, -1.6) {$C$};
                \node [style=site] (AA) at (4, 0.8) {$AA$};
                \node [style=site] (AB) at (4, -0.8) {$AB$};
                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
                \node [style=transition] (tau4) at (10, 0) {$\delta$};

                \node [scale=3] (Q) at (12, -6) {$\C$};
                \node [style=site, fill=blue!20] (W) at (-4, -6) {$W$};
                \node [style=site, draw=ForestGreen] (X) at (0, -6) {$X$};
                \node [style=site, draw=ForestGreen] (Y) at (4, -6) {$Y$};
                \node [style=site, draw=ForestGreen] (Z) at (8, -6) {$Z$};
                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
                \node [style=transition, draw=ForestGreen] (tau6) at (2, -6) {$\chi$};
                \node [style=transition, draw=ForestGreen] (tau7) at (6, -6) {$\psi$};
                \node [style=transition, draw=ForestGreen] (tau8) at (10, -6) {$\omega$};

@@

                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
                \draw [style=arrow, draw=ForestGreen, bend left=15] (X) to (tau6);
                \draw [style=arrow, draw=ForestGreen, bend right=15] (X) to (tau6);
                \draw [style=arrow, draw=ForestGreen] (tau6) to (Y);
                \draw [style=arrow, draw=ForestGreen, bend left=20] (Y) to (tau7);
                \draw [style=arrow, draw=ForestGreen] (Y) to (tau7);
                \draw [style=arrow, draw=ForestGreen, bend right=20] (Y) to (tau7);
                \draw [style=arrow, draw=ForestGreen] (tau7) to (Z);
                \draw [style=arrow, draw=ForestGreen, bend left=50] (tau7.south) to (Y.south);
                \draw [style=arrow, draw=ForestGreen] (Z) to (tau8);
                \draw [style=arrow, draw=ForestGreen, bend left=30] (tau8) to (X);
                \draw [style=arrow, draw=ForestGreen, bend right=30] (tau8) to (X);
                \draw [style=arrow, draw=ForestGreen, bend right=30] (tau8) to (Y);

                \draw [style=sitemap, bend right=30] (A) to (X);
                \draw [style=sitemap, bend right=30] (B) to (X);
                \draw [style=sitemap, bend right=30] (AA) to (Y);
                \draw [style=sitemap, bend right=30] (AB) to (Y);
                \draw [style=sitemap, bend right=30] (C) to (Y);
                \draw [style=sitemap, bend right=30] (AAAB) to (Z);
                \draw [style=transitionmap, bend right=30] (tau1) to (tau6);
                \draw [style=transitionmap, bend right=30] (tau2) to (tau6);
                \draw [style=transitionmap, bend right=30] (tau3) to (tau7);
                \draw [style=transitionmap, bend right=30] (tau4) to (tau8);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}
were we've chosen $\{A,B,C\}$ and $\{W\}$ as the generating sets (in fact, bases) for $\A$ and $\C$, respectively.
Of particular note here is that $f(\A)$ (outlined in red) is a subspace of $\C$.
It will always be the case that the image of an assembly space will be a subspace of the codomain.
\begin{theorem}\label{lem:assembly-image-is-subspace}
    If $f : A \rightarrow B$ is an assembly map between assembly spaces $A$ and $B$, then $f(A)$ is an assembly subspace of $B$.
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}
While $f(\A)$ is a subspace of $\C$, it is decidedly not rooted in $\C$.
However, by highlighting a rooted subspace of $\A$ we see that the image of that subspace is rooted in $f(\A)$.
\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [scale=3] (P) at (12, 0) {$\A$};
                \node [style=site, fill=blue!20, draw=red, line width=1.5] (A) at (0, 0.8) {$A$};
                \node [style=site, fill=blue!20, draw=red, line width=1.5] (B) at (0, -0.8) {$B$};
                \node [style=site] (C) at (6, -1.6) {$C$};
                \node [style=site, draw=red, line width=1.5] (AA) at (4, 0.8) {$AA$};
                \node [style=site, draw=red, line width=1.5] (AB) at (4, -0.8) {$AB$};
                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition, draw=red, line width=1.5] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition, draw=red, line width=1.5] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
                \node [style=transition] (tau4) at (10, 0) {$\delta$};

                \node [scale=3] (Q) at (12, -6) {$\C$};
                \node [style=site, fill=blue!20] (W) at (-4, -6) {$W$};
                \node [style=site, draw=red, line width=1.5] (X) at (0, -6) {$X$};
                \node [style=site, draw=red, line width=1.5] (Y) at (4, -6) {$Y$};
                \node [style=site, draw=ForestGreen] (Z) at (8, -6) {$Z$};
                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
                \node [style=transition, draw=red, line width=1.5] (tau6) at (2, -6) {$\chi$};
                \node [style=transition, draw=ForestGreen] (tau7) at (6, -6) {$\psi$};
                \node [style=transition, draw=ForestGreen] (tau8) at (10, -6) {$\omega$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, draw=red, line width=1.5, bend right=15] (A) to (tau1);
                \draw [style=arrow, draw=red, line width=1.5, bend left=15] (A) to (tau1);
                \draw [style=arrow, draw=red, line width=1.5, bend right=15] (A) to (tau2);
                \draw [style=arrow, draw=red, line width=1.5] (tau1) to (AA);
                \draw [style=arrow, draw=red, line width=1.5] (B) to (tau2);
                \draw [style=arrow, draw=red, line width=1.5] (tau2) to (AB);
                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
                \draw [style=arrow, draw=gray!80] (AAAB) to (tau4);
                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (A);
                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (AA);
                \draw [style=arrow, draw=gray!80, bend left=40] (tau4) to (B);

                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
                \draw [style=arrow, draw=red, line width=1.5, bend left=15] (X) to (tau6);
                \draw [style=arrow, draw=red, line width=1.5, bend right=15] (X) to (tau6);
                \draw [style=arrow, draw=red, line width=1.5] (tau6) to (Y);
                \draw [style=arrow, draw=ForestGreen, bend left=20] (Y) to (tau7);
                \draw [style=arrow, draw=ForestGreen] (Y) to (tau7);
                \draw [style=arrow, draw=ForestGreen, bend right=20] (Y) to (tau7);
                \draw [style=arrow, draw=ForestGreen] (tau7) to (Z);
                \draw [style=arrow, draw=ForestGreen, bend left=50] (tau7.south) to (Y.south);
                \draw [style=arrow, draw=ForestGreen] (Z) to (tau8);
                \draw [style=arrow, draw=ForestGreen, bend left=30] (tau8) to (X);
                \draw [style=arrow, draw=ForestGreen, bend right=30] (tau8) to (X);
                \draw [style=arrow, draw=ForestGreen, bend right=30] (tau8) to (Y);

                \draw [style=sitemap, opacity=0.5,  bend right=30] (A) to (X);
                \draw [style=sitemap, opacity=0.5,  bend right=30] (B) to (X);
                \draw [style=sitemap, opacity=0.5,  bend right=30] (AA) to (Y);
                \draw [style=sitemap, opacity=0.5,  bend right=30] (AB) to (Y);
                \draw [style=sitemap, opacity=0.5,  bend right=30] (C) to (Y);
                \draw [style=sitemap, opacity=0.5,  bend right=30] (AAAB) to (Z);
                \draw [style=transitionmap, opacity=0.5,  bend right=30] (tau1) to (tau6);
                \draw [style=transitionmap, opacity=0.5,  bend right=30] (tau2) to (tau6);
                \draw [style=transitionmap, opacity=0.5,  bend right=30] (tau3) to (tau7);
                \draw [style=transitionmap, opacity=0.5,  bend right=30] (tau4) to (tau8);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}
This too will always be the case: the image of a rooted subspace will always be rooted in the image.
\begin{theorem}\label{thm:rooted-image}
    Let $A$ be an assembly space, $Z \subseteq A$ a rooted assembly subspace, and $f : A \rightarrow B$ an assembly map.
    Then $(f(Z), S(f)(G_Z))$ is rooted in $(f(A), S(f)(G_A)$.
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}
The interaction of assembly maps and rooted subspaces will allow us to establish bounds on the assembly index, defined in the next section, by considering the image of the space under some map.
These bounds will be useful in situations where determining the assembly index of some object is computationally infeasible.

@@

The assembly index, as we have defined it, is dependent on the choice of generating set.
To make this point clear, we will first consider the example assembly space $\A$ and present the assembly index and a representative minimal assembly subspace for each site.
\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [scale=3] (P) at (1, 9) {$\A$};
                \node [style=site, fill=blue!20] (A) at (0, 7.4) {$A$};
                \node [style=site, fill=blue!20] (B) at (0, 5.8) {$B$};
                \node [style=site, fill=blue!20] (C) at (6, 5) {$C$};
                \node [style=site] (AA) at (4, 7.4) {$AA$};
                \node [style=site] (AB) at (4, 5.8) {$AB$};
                \node [style=site] (AAAB) at (8, 6.6) {$AAAB$};
                \node [style=transition] (alpha) at (2, 7.4) {$\alpha$};
                \node [style=transition] (beta) at (2, 5.8) {$\beta$};
                \node [style=transition] (gamma) at (6, 6.6) {$\gamma$};
                \node [style=transition] (delta) at (10, 6.6) {$\delta$};

                \node [style=site, fill=blue!20] (A0) at (0, 0) {$A$};
                \node [scale=2] at (0, -2) {$c_\A(A) = 0$};

                \node [style=site, fill=blue!20] (B1) at (4, 0) {$B$};
                \node [scale=2] at (4, -2) {$c_\A(B) = 0$};

                \node [style=site, fill=blue!20] (C2) at (8, 0) {$C$};
                \node [scale=2] at (8, -2) {$c_\A(C) = 0$};

                \node [style=site, fill=blue!20] (A3) at (12, 0) {$A$};
                \node [style=transition] (alpha3) at (12, 2) {$\alpha$};
                \node [style=site] (AA3) at (12, 4) {$AA$};
                \node [scale=2] at (12, -2) {$c_\A(AA) = 1$};

                \node [style=site, fill=blue!20] (A4) at (16, 0) {$A$};
                \node [style=site, fill=blue!20] (B4) at (17.6, 0) {$B$};
                \node [style=transition] (beta4) at (16.8, 2) {$\beta$};
                \node [style=site] (AB4) at (16.8, 4) {$AB$};
                \node [scale=2] at (16.8, -2) {$c_\A(AB) = 1$};

                \node [style=site, fill=blue!20] (A5) at (21.6, 0) {$A$};
                \node [style=site, fill=blue!20] (B5) at (23.2, 0) {$B$};
                \node [style=transition] (alpha5) at (21.6, 2) {$\alpha$};
                \node [style=transition] (beta5) at (23.2, 2) {$\beta$};
                \node [style=site] (AA5) at (21.6, 4) {$AA$};
                \node [style=site] (AB5) at (23.2, 4) {$AB$};
                \node [style=site, fill=blue!20] (C5) at (24, 6) {$C$};
                \node [style=transition] (gamma5) at (22.4, 6) {$\gamma$};
                \node [style=site] (AAAB5) at (22.4, 8) {$AAAB$};
                \node [scale=2] at (22.4, -2) {$c_\A(AAAB) = 3$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend right=15] (A) to (alpha);
                \draw [style=arrow, bend left=15] (A) to (alpha);
                \draw [style=arrow] (alpha) to (AA);
                \draw [style=arrow, bend right=15] (A) to (beta);
                \draw [style=arrow] (B) to (beta);
                \draw [style=arrow] (beta) to (AB);
                \draw [style=arrow] (AA) to (gamma);
                \draw [style=arrow] (AB) to (gamma);
                \draw [style=arrow, bend left=30] (C) to (gamma);
                \draw [style=arrow, bend left=30] (gamma) to (C);
                \draw [style=arrow] (gamma) to (AAAB);
                \draw [style=arrow] (AAAB) to (delta);
                \draw [style=arrow, bend right=30] (delta) to (A);
                \draw [style=arrow, bend right=30] (delta) to (AA);
                \draw [style=arrow, bend left=40] (delta) to (B);

                \draw [style=arrow, bend left=15] (A3) to (alpha3);
                \draw [style=arrow, bend right=15] (A3) to (alpha3);
                \draw [style=arrow] (alpha3) to (AA3);

                \draw [style=arrow] (A4) to (beta4);
                \draw [style=arrow] (B4) to (beta4);
                \draw [style=arrow] (beta4) to (AB4);

                \draw [style=arrow, bend left=15] (A5) to (alpha5);
                \draw [style=arrow, bend right=15] (A5) to (alpha5);
                \draw [style=arrow] (alpha5) to (AA5);
                \draw [style=arrow, bend right=15] (A5) to (beta5);
                \draw [style=arrow] (B5) to (beta5);
                \draw [style=arrow] (beta5) to (AB5);
                \draw [style=arrow] (AA5) to (gamma5);
                \draw [style=arrow] (AB5) to (gamma5);
                \draw [style=arrow, bend left=30] (C5) to (gamma5);
                \draw [style=arrow, bend left=30] (gamma5) to (C5);
                \draw [style=arrow] (gamma5) to (AAAB5);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}
However, if we were to have chosen a different generating set, say $\{C, AAAB\}$, while retaining the same underlying Petri net the results would have been quite different.
\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [scale=3] (P) at (1, 10.2) {$\A'$};
                \node [style=site, fill=blue!20] (AAAB) at (0, 7.8) {$AAAB$};
                \node [style=transition] (delta) at (2, 7.8) {$\delta$};
                \node [style=site] (A) at (4, 8.6) {$A$};
                \node [style=site] (B) at (4, 7.0) {$B$};
                \node [style=transition] (alpha) at (6, 8.6) {$\alpha$};
                \node [style=transition] (beta) at (6, 7.0) {$\beta$};
                \node [style=site] (AA) at (8, 8.6) {$AA$};
                \node [style=site] (AB) at (8, 7.0) {$AB$};
                \node [style=site, fill=blue!20] (C) at (10, 9.4) {$C$};
                \node [style=transition] (gamma) at (10, 7.8) {$\gamma$};

                \node [style=site, fill=blue!20] (AAAB0) at (0, 0) {$AAAB$};
                \node [scale=2] at (0, -2) {$c_{\A'}(AAAB) = 0$};

                \node [style=site, fill=blue!20] (C1) at (6, 0) {$C$};
                \node [scale=2] at (6, -2) {$c_{\A'}(C) = 0$};

                \node [style=site, fill=blue!20] (AAAB2) at (13.6, 0) {$AAAB$};
                \node [style=transition] (delta2) at (13.6, 2) {$\delta$};
                \node [style=site] (A2) at (12, 4) {$A$};
                \node [style=site] (B2) at (13.6, 4) {$B$};
                \node [style=site] (AA2) at (15.2, 4) {$AA$};
                \node [scale=2] at (13.6, -2) {$c_{\A'}(A) = c_{\A'}(B) = c_{\A'}(AA) = 1$};

                \node [style=site, fill=blue!20] (AAAB3) at (22, 0) {$AAAB$};
                \node [style=transition] (delta3) at (22, 2) {$\delta$};
                \node [style=site] (A3) at (21.2, 4) {$A$};
                \node [style=site] (B3) at (22.8, 4) {$B$};
                \node [style=site] (AA3) at (23.6, 2) {$AA$};
                \node [style=transition] (beta3) at (22, 6) {$\beta$};
                \node [style=site] (AB3) at (22, 8) {$AB$};
                \node [scale=2] at (22, -2) {$c_{\A'}(AB) = 2$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow] (AAAB) to (delta);
                \draw [style=arrow] (delta) to (A);
                \draw [style=arrow, bend left=40] (delta.north) to (AA);
                \draw [style=arrow] (delta) to (B);
                \draw [style=arrow, bend right=15] (A) to (alpha);
                \draw [style=arrow, bend left=15] (A) to (alpha);
                \draw [style=arrow] (alpha) to (AA);
                \draw [style=arrow, bend right=15] (A) to (beta);
                \draw [style=arrow] (B) to (beta);
                \draw [style=arrow] (beta) to (AB);
                \draw [style=arrow] (AA) to (gamma);
                \draw [style=arrow] (AB) to (gamma);
                \draw [style=arrow, bend right=30] (C) to (gamma);
                \draw [style=arrow, bend right=30] (gamma) to (C);
                \draw [style=arrow, bend left=40] (gamma.south) to (AAAB);

                \draw [style=arrow] (AAAB2) to (delta2);
                \draw [style=arrow] (delta2) to (AA2);
                \draw [style=arrow] (delta2) to (A2);
                \draw [style=arrow] (delta2) to (B2);

                \draw [style=arrow] (AAAB3) to (delta3);
                \draw [style=arrow] (delta3) to (A3);
                \draw [style=arrow] (delta3) to (B3);
                \draw [style=arrow] (delta3) to (AA3);
                \draw [style=arrow] (A3) to (beta3);
                \draw [style=arrow] (B3) to (beta3);
                \draw [style=arrow] (beta3) to (AB3);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}
While this may seem, at first glance, to be undesirable it captures a very important point about the assembly process: the materials that you start with greatly influence how difficult, complex or costly assembling a given object may be.
The cases of interest in this work presume that we being with only ``simple" objects from which we aim to build more ``complex" objects.
However, the formalism, in and of itself, it far more general than this.

We now turn our attention to the task of determining the assembly index of an object.
In practical terms, this requires an algorithm for computing the assembly index relative to some space.
In this work, we do not present a general algorithm to do so, though a simple depth-first search of the space may suffice in some cases.
Rather, we first show that the assembly index is in fact computable, and subsequently establish methods of bounding the assembly index in cases where direct calculation is infeasible.
\begin{theorem}\label{thm:computable}
    If $A$ is an assembly space and $x \in S(A)$ is finite, then $c(x)$ is computable.
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}
Of course, just because the value is computable does not mean that it can be computed in reasonable time.
In fact, the general problem is likely to be \texttt{NP}-hard.
In situtations where direct computation is infeasible, we can resort to bounding the value of the assembly index by computing the index in an analogous space.
The first of the bounds we present is an upper bound determined by computing the assembly index in a subspace containing the site.
\begin{theorem}\label{thm:subspace-index-upper-bound}
    Let $(A, G_A)$ be an assembly space and let $(B, G_A)$ be a rooted assembly subspace of $A$.
    For every finite $b \in S(B)$, the assembly index of $b$ in $B$ is at least the assembly index of $b$ in $A$.
    That is, $c_B(b) \ge c_A(b)$ for all $b \in S(B)$
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}

The the remaining examples, we will depart from using $\A$ since large enough to demonstrate the desired points.
Consider the assembly space and subspace depicted below:
\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site, fill=blue!20] (A) at (0, 0) {$A$};
                \node [style=site] (B) at (4, 0) {$B$};
                \node [style=site] (C) at (8, 0) {$C$};
                \node [style=site] (D) at (12, 0) {$D$};
                \node [style=site] (E) at (16, 0) {$E$};
                \node [style=site] (F) at (20, 0) {$F$};
                \node [style=transition] (a) at (2, 0) {$\alpha$};
                \node [style=transition] (b) at (6, 0) {$\beta$};
                \node [style=transition] (c) at (10, 0) {$\gamma$};
                \node [style=transition] (d) at (14, 0) {$\delta$};
                \node [style=transition] (e) at (18, 0) {$\epsilon$};
                \node [style=transition] (f) at (8, 2) {$\zeta$};
                \node [style=transition] (g) at (12, -4) {$\eta$};
                \node [style=transition] (h) at (16, -3) {$\theta$};
                \node [style=transition] (i) at (14, 3) {$\iota$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend left=25, draw=gray!70] (B) to (f);
                \draw [style=arrow, bend left=10, draw=gray!70] (B) to (f);
                \draw [style=arrow, bend left=25, draw=gray!70] (f) to (D);

                \draw [style=arrow, bend right=10, draw=gray!80] (B) to (g);
                \draw [style=arrow, bend right=10, draw=gray!80] (C) to (g);
                \draw [style=arrow, bend right=10, draw=gray!80] (g) to (E);

                \draw [style=arrow, bend right=10, draw=gray!90] (B) to (h);
                \draw [style=arrow, bend right=10, draw=gray!90] (D) to (h);
                \draw [style=arrow, bend right=10, draw=gray!90] (h) to (F);

                \draw [style=arrow, bend left=25, draw=gray!80] (C) to (i);
                \draw [style=arrow, bend left=10, draw=gray!80] (C) to (i);
                \draw [style=arrow, bend left=25, draw=gray!80] (i) to (F);

                \draw [style=arrow, draw=red, bend left=15] (A) to (a);
                \draw [style=arrow, draw=red, bend right=15] (A) to (a);
                \draw [style=arrow, draw=red, bend right=30] (A) to (b);
                \draw [style=arrow, draw=red, bend right=30] (A) to (c);
                \draw [style=arrow, draw=red, bend right=30] (A) to (d);
                \draw [style=arrow, draw=red, bend right=30] (A) to (e);
                \draw [style=arrow, draw=red] (a) to (B);
                \draw [style=arrow, draw=red] (B) to (b);
                \draw [style=arrow, draw=red] (b) to (C);
                \draw [style=arrow, draw=red] (C) to (c);
                \draw [style=arrow, draw=red] (c) to (D);
                \draw [style=arrow, draw=red] (D) to (d);
                \draw [style=arrow, draw=red] (d) to (E);
                \draw [style=arrow, draw=red] (E) to (e);
                \draw [style=arrow, draw=red] (e) to (F);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}
The edges associated with an assembly subspace are highlighed in red.
If we consider the site $F$ in the context of the space, as a whole, the assembly index is $c(F) = 3$.
There are two minimal, rooted assembly subspaces with that size which contain either $\alpha$, $\zeta$ and $\eta$; or $\alpha$, $\beta$ and $\theta$; as transitions.
However, if we've restricted ourselves only the the subspace, then $\zeta$, $\eta$ and $\theta$ are inadmissible.
As such, the assembly index in the subspace is $5$.
